\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

% Font options - uncomment your preferred font
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
\usepackage[default]{lato}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADER----------
\begin{center}
    \textbf{\Huge \scshape Andre Udegbe} \\ \vspace{1pt}
    \small 585-957-4760 $|$ \href{mailto:andreoudegbe@gmail.com}{\underline{andreoudegbe@gmail.com}} $|$ 
    \href{https://linkedin.com/in/andreudegbe}{\underline{linkedin.com/in/andreudegbe}}
\end{center}

%----------TITLE----------
\begin{center}
    \textbf{\large SENIOR TECHNICAL PRODUCT MANAGER $|$ SALES ENABLEMENT \& PLATFORM STRATEGY}
\end{center}


%-----------SUMMARY-----------
\section{Summary}
  \small{Proven Product Leader with 10+ years bridging strategic vision and technical execution across enterprise platforms. Expert in orchestrating cross-functional teams to deliver scalable solutions that drive measurable business outcomes. Specialized in end-to-end platform transformation and translating complex architectures into compelling product narratives, reducing time-to-market by 65\% and equipping sales teams with stable, high-performance demo environments that accelerated revenue by \$1.2M.}


%-----------CORE COMPETENCIES-----------
\section{Core Competencies}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Strategy \& Enablement}{: Technical Storytelling, Demo Environment Strategy, Sales Enablement, GTM \& Product Alignment, Cross-Functional Leadership} \\
     \textbf{Technical}{: Platform Orchestration, Enterprise API Strategy, Real-time Observability, Cloud Infrastructure (AWS/Azure), Zero Trust Security}
    }}
 \end{itemize}


%-----------EXPERIENCE-----------
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {ITX Corp}{Jan 2023 -- Present}
      {Senior Technical Product Manager -- AI Automation \& Platform Strategist}{}
      \resumeItemListStart
        \resumeItem{\textbf{Sales Enablement \& Revenue:} Accelerated sales pipeline by \$1.2M by integrating AI analytics with Salesforce, providing sales engineers with real-time "killer feature" data points that improved lead conversion rates by 28\%.}
        \resumeItem{\textbf{Demo Environment Stability:} Stabilized product demo environments by implementing AI-driven threat detection, ensuring 99.9\% availability for critical client presentations and reducing friction during GTM launches.}
        \resumeItem{\textbf{Storytelling \& Communication:} Presented technical progress monthly to C-level executives, translating complex AI automation concepts into actionable business insights and strategic recommendations that resonated with non-technical stakeholders.}
        \resumeItem{\textbf{Cross-Functional Orchestration:} Orchestrated alignment across 20+ engineers and 4 specialized teams (AI/ML, Security, DevOps, Platform) to deliver scalable solutions, ensuring a unified "better together" product story.}
        \resumeItem{\textbf{Governance \& Standards:} Established governance for product simulation environments, ensuring that sales and field teams had access to consistent, updated, and reliable datasets for client demonstrations.}
        \resumeItem{\textbf{End-to-End User Journey:} Automated 70\% of critical workflows by integrating Kore.ai with existing systems, enhancing the user experience and enabling \$850K in annual operational savings.}
      \resumeItemListEnd

    \resumeSubheading
      {Intellor Group}{June 2021 -- Jan 2023}
      {Technical Product Manager -- Cloud and Audio Platforms Orchestration}{}
      \resumeItemListStart
        \resumeItem{\textbf{Client Experience:} Increased client satisfaction (NPS) by 60\% through a zero-disruption migration strategy for 200+ enterprise accounts, ensuring the product experience remained seamless and reliable for end-users.}
        \resumeItem{\textbf{Reliability \& Observability:} Improved incident response by 40\% via real-time observability and automated monitoring dashboards, establishing the stability required for high-stakes customer demonstrations.}
        \resumeItem{\textbf{Modular Delivery:} Accelerated feature delivery by 45\% using modular architecture, enabling rapid deployment of tailored solutions across HR, Legal, and Government verticals.}
        \resumeItem{\textbf{Infrastructure Optimization:} Achieved 99.99\% uptime while reducing vendor costs by 30\% through strategic AWS infrastructure implementation, ensuring a robust platform foundation.}
      \resumeItemListEnd

    \resumeSubheading
      {KraftHouse Ltd}{Aug 2018 -- June 2021}
      {Product Manager -- Digital Platform Strategy}{}
      \resumeItemListStart
        \resumeItem{\textbf{User Journey Optimization:} Boosted partner sales by 27\% within 90 days by automating personalized user journeys based on behavioral segmentation, effectively demonstrating the right value to the right user at the right time.}
        \resumeItem{\textbf{Data-Driven Engagement:} Increased user retention by 34\% through data-driven loyalty experiences and hyper-targeted promotions, utilizing real-time analytics to refine the product story.}
        \resumeItem{\textbf{Influence Without Authority:} Managed a team of 12 from ideation through successful launch, ensuring on-time delivery under a \$1.2M budget through meticulous planning and coordination.}
      \resumeItemListEnd

    \resumeSubheading
      {Acme Energy}{Dec 2014 -- Aug 2018}
      {Software Engineer -- Enterprise Logistics Platforms}{}
      \resumeItemListStart
        \resumeItem{Reduced transit delays by 35\% through predictive scheduling and GPS-based automation, creating tangible value stories for logistics operations.}
        \resumeItem{Enhanced operational efficiency via enterprise application refactoring and CI/CD pipeline automation, building the technical rigor required for scalable product growth.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------STRATEGIC PROJECTS-----------
\section{Strategic Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Powered User Behavior Prediction Platform} $|$ \emph{ITX Corp}}{2025}
          \resumeItemListStart
            \resumeItem{\textbf{Impact:} Enhanced sales forecasting, 17\% reduction in customer churn.}
            \resumeItem{\textbf{Detail:} Led cross-functional initiative building secure data pipelines where AI/ML models delivered actionable insights to Salesforce, directly supporting proactive retention strategies and predictive sales intelligence.}
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{Secure Client-Facing API Portal Launch} $|$ \emph{ITX Corp}}{2024}
          \resumeItemListStart
            \resumeItem{\textbf{Impact:} HIPAA-compliant automation, 65\% reduction in attack surface.}
            \resumeItem{\textbf{Detail:} Designed and implemented comprehensive API security architecture, establishing automated authentication standards that improved API response times by 47\%.}
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{Enterprise API Ecosystem Automation} $|$ \emph{ITX Corp}}{2023}
          \resumeItemListStart
            \resumeItem{\textbf{Impact:} 70\% reduction in onboarding time, enhanced Developer Experience (DevX).}
            \resumeItem{\textbf{Detail:} Led design and rollout of a robust API Management Platform with a Developer Portal, supporting internal/external developers and establishing standards that improved the overall product ecosystem.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------EDUCATION & CERTIFICATIONS-----------
\section{Education \& Certifications}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of the Cumberlands}{Expected 2026}
      {Masters of Science in Data Science}{}
    \resumeSubheading
      {Rochester Institute of Technology}{2022}
      {Masters of Science in Human Computer Interaction}{}
    \resumeSubheading
      {Babcock University}{2014}
      {Bachelor of Science in Computer Science}{}
    \resumeSubheading
      {}{}{}{}
  \resumeSubHeadingListEnd

  \vspace{-12pt}
  
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Certifications}{: Certified Scrum Product Owner (CSPO), Certified Scrum Master (CSM), SAFe Scrum Master (SSM), Certified Information Security Manager (CISM), AWS Solutions Architect Associate, Microsoft Azure Solutions Architect Expert}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
